---
title: "HW2 Telemarketing"
author: "Daniel Vasquez"
date: "11/08/2020"
output:
  html_document:
    toc: true
    theme: readable
    highlight: tango
    code_folding: hide
---
```{r}
library(caret)
library(e1071)
library(neuralnet)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Downloading and Prepping the Data

```{r}
#Downloading and Prepping the Data
tele <- read.csv("tele.csv", stringsAsFactors = TRUE)
summary(tele)

#We are deleting the "duration" variable because it is an after the fact measurement. We only should be using variables that we know before the call
tele$duration <- NULL

# Deleting the column X
tele$X <- NULL

# Changing pdays to a dummy and deleting pdays
tele$pdaysdummy <- ifelse(tele$pdays == 999, 0, 1)
tele$pdays <- NULL

str(tele)
```

## Getting Data Ready for Analysis

```{r}
# Using model.matrix to convert all the factors to dummy variables
# We are converting all of the factors into dummy variables as the input into ANN has to be numeric

telemm <- as.data.frame(model.matrix(~.-1,tele))
str(telemm)

# Randomize the rows in the data (shuffling the rows)
set.seed(12345)
tele_random <- telemm[sample(nrow(telemm)),]

#Normalize the data
normalize <- function(x) {
  return ((x - min(x)) / (max(x) - min(x)))
}

# we are going to normalize everything 
tele_norm <- as.data.frame(lapply(tele_random, normalize))
```


## Getting Train and Test Samples

```{r}
# Selects 10000 random rows for test data
set.seed(12345)
test_set <- sample(1:nrow(tele_norm), 10000) 
# Depending on R-version and computer, different rows may be selected. 
# If that happens, results are different. 

# Create a train set and test set
#First the predictors - all columns except the yyes column
tele_train <- tele_norm[-test_set, ]
tele_test <- tele_norm[test_set, ]
```

> Now you are ready to build your ANN model. Feel free to modify the data load, cleaning and preparation code above as per your preference.

## 01 Logistic Regression Model
```{r, cache=TRUE}
tele_LR <- glm(yyes ~ ., data = tele_train, family = binomial(link = "logit"))
summary(tele_LR)
# Summary indicated irrelevant variables
```

## 02 Stepwise Regression [Data Refinement]
```{r, cache=TRUE}
# Creation of model
tele_step <- step(tele_LR, direction="backward")
summary(tele_step)

#Evaluation matrix. 50% prediction level for classification of a calls = YES.

p_step <- predict(tele_step, tele_test, type = "response")
p_cat <- ifelse(p_step >= 0.5, 1, 0)
```

## 03 Prediction w/ StepWise Regression Eval
```{r, cache=TRUE}
tele_test$p <- ifelse(p_step >= 0.5, 1, 0)
tele_test$p <- as.factor(tele_test$p)

str(tele_test$p)
str(as.factor(tele_test$yyes))
```

## 04 Evaluation Matrix
```{r}
confusionMatrix(as.factor(p_cat), as.factor(tele_test$yyes), positive = "1")
```


## 05A ANN MODEL
```{r, cache=TRUE}
# model 1: Initial ANN model using one hidden neuron

tele_ANN1 <- neuralnet(formula = yyes ~ ., data = tele_train)
plot(tele_ANN1)
# model 1 :results
tele_ANN1_results <- compute(tele_ANN1, tele_test[-53])

# model 1: predicted strength values
p_yes <- ifelse(tele_ANN1_results$net.result > .5, 1, 0)
head(p_yes)

# model 1 matrix
confusionMatrix(as.factor(p_yes), as.factor(tele_test$yyes), positive="1")

```


## 05B ANN Model w/ called LR Variables

```{r, cache=TRUE}
# removed family from call

tele_ANN2 <- neuralnet(formula = yyes ~ jobblue.collar + jobretired + jobservices + 
    jobstudent + maritalsingle + educationbasic.6y + educationuniversity.degree + 
    defaultunknown + contacttelephone + monthaug + monthdec + 
    monthjun + monthmar + monthmay + monthnov + day_of_weekmon + 
    day_of_weekthu + day_of_weekwed + campaign + poutcomenonexistent + 
    poutcomesuccess + emp.var.rate + cons.price.idx + cons.conf.idx + 
    euribor3m + nr.employed + pdaysdummy, data = tele_train)

# Model 2: results
tele_ANN2_results <- compute(tele_ANN2, tele_test[-53])

#Model 2: Predicted Strength Values
p_yes2 <- ifelse(tele_ANN2_results$net.result > 0.5, 1, 0)
head(p_yes2)

#model 2 matrix
confusionMatrix(as.factor(p_yes2), as.factor(tele_test$yyes), positive="1")
```

## Conclusion

I would leverage the logistical regression model because of transparency of the significant variables. The logistical regression model can tell me which variables are most significant in terms of predicting a positive response rate whereas the ANN model does not provide insights I can use for quality improvement. Accuracy matters less than insights in this assignment. The ANN model could likely yield more accurate predictive results but increase development time resources and analysis. A follow-up research proposal, if requested, can be sent to informatics department.

